Introduction to latent means models in R

### 2024-01-25 README.qmd
Organize materials better (?)
Update README smore

@@

@@

Contributions preferably via pull requests.

>>>>

# Modify environment variables in .Renviron.example & rename it to .Renviron

@@

Once the computations are finished the rendered documents are in docs/.

@@

Contributions preferably via pull requests. You can also grab the rendered manuscript (Word, PDF) from the latest [release](https://github.com/mvuorre/latent-mean-centering-ms/releases) for comments & edits.
